---
title: "new_repository"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
library(tidyverse)

samp = rnorm(100)
length(samp)

plot_df = tibble(
  x = rnorm(100),
  y = 1 + 2 ^ x + rnorm(100)
)

z = 1
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
- this allows you to execute small pieces of R in the comments section
The number of rows in `plot_df` is `r nrow(plot_df)`

- See class notes for all additions to '''{r ...} you can add to change up the code chunks
- You can name the code chunks, helpful way to determine where issues are coming from
- Hot key for adding rmd chunk command-option-i
```{r generate_mean, eval=FALSE}
mean(samp)
```

Learning Assessment 1
```{r learning_assessment, warning=FALSE}
df = tibble(
  a = rnorm(500, mean = 1),
  b = a > 0,
  c = abs(a)
)

ggplot(df, aes(c)) + geom_histogram()
```
```{r, echo=FALSE}
med = median(pull(df, c))
```

The median of the sample from the dataframe `df` is `r round(med, digits = 2)`.

Formatting Text

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

YAML and Output Formats 




